

You must write a one-page proposal before you actually begin your project in-depth. These will be submitted via Compass and are due Wednesday, March 31 at 11:59pm.

In the proposal, you should (1) indicate the track of your project (i.e., research track, software track, or startup track), (2) address the following questions, (3) include the names and email addresses of all the team members, and (4) identify the coordinator of the project in case the team has more than one member, who would take the primary responsibility of coordinating the work of all team members; the coordinator is also our primary contact for providing feedback about the project.

As long as these questions are addressed, the proposal does not have to be very long. A couple of sentences for each question would be sufficient.

If your project is aiming at the research track, you should focus on the following in your proposal:

[Research Question] What is your research question? Clearly define the research problem/question.
[Significance] Why is this an interesting question to ask and why would we care about the answer to this question or a solution to the problem?
[Novelty] Has any existing research work tried to answer the same or a similar question, and if so, what is still unknown? (In other words, what is the novelty of your research question?) Provide a brief list of related work.
[Approach] How do you plan to work out the answer to the question? (At the proposal stage, you are only expected to have a sketch of your methods.)
[Evaluation] How would you evaluate your solution? That is, how do you plan to demonstrate that your solution/answer is good or is reasonable?
[Timeline] A rough timeline to show when you expect to finish what. List a couple of milestones if possible (they can be tentative).
[Task division] Use one sentence to describe what each team member is expected to work on (can be tentative). 